Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-09 W13report.tex
Reordering of author list .

\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen\vspace{-2ex}}
\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
\date{\vspace{-2ex}\today}

>>>>

\author{
Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
Russell Owen (UW), Paul Price (Princeton), Robert Lupton (Princeton), \\
Dustin Lang (CMU), Jim Bosch (Princeton), Robyn Allsman (LSSTC), \\
Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU), \\
Scott Daniel (UW), Greg Daues (NCSA), Gregory Dubois-Felsmann (SLAC), \\
Mike Freemon (NCSA),Perry Gee (UC Davis), Bill Glick (NCSA),\\
Steve Groom (IPAC),Joshua Hoblitt (NOAO), Mario Juric (LSSTC),\\ 
Jeff Kantor (LSSTC),Ron Lambert (NOAO), Kian-Tat Lim (SLAC),\\
Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\
Dick Shaw (NOAO), Douglas Smith (SLAC), Schuyler Van Dyk (IPAC), \\
and Daniel Wang (SLAC)\\ 
{\it for LSST Data Management}
\vspace{-2ex}}
\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
\date{\today}
